A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-01-29 papers/execution-model/model.tex
Add files via upload
Add some more to Motivation (blue line)

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}

@@

@@

>>>>

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{listings}
\usepackage{xcolor}

@@

{\color{blue} Let us consider how this auction contract could be written in Michelson, the language of smart contracts in Tezos. The state of a smart contract is presented by the data in its storage on the blockchain. The input data provided with a contract invocation is specified as a parameter.

\begin{lstlisting}[numbers=none]
parameter (or (unit %close)
              (mutez %bid)); # participant's bid
storage (pair
              (pair bool address)  # is bidding allowed,
               contract owner's address
              (pair mutez address) # current highest bid
               and bidder's address
        );
\end{lstlisting}

where \texttt{unit} is the type whose only value is \texttt{Unit}, \texttt{mutez} is a specific type for manipulating tokens in Tezos, and \texttt{pair} is a pair of values a and b of types (l) and (r) written as (\texttt{Pair a b}).

There are two purposes for calling an auction contract: (1) a bid by a bidder, or (2) a contract closing by the contract owner. Michelson supports multiple entrypoints, distinguished by \texttt{or}. The contract's storage on the blockchain contains two pairs, the first pair containing the flag indicating whether bidding is allowed or the contract is closed and the address of the contract owner, and the second pair containing the current highest bid and the address of the bidder. Michelson is stack-based. It takes a pair of the parameter and the current storage as inputs and returns the updated storage and a list of internal operations. When a bidder invokes the contract to bid, its bid and address are updated in the storage if its bid is higher than the current highest bid, otherwise they are discharged. The closing of the contract is called by the contract owner when it reaches 48 hours }

@@

{\color{blue} In contrast, these tasks are able to implement as programs that interact with the blockchain.  We call the function that deploy a contract \texttt{originate-contract}, and the function that invokes a contract \texttt{call-contract}. The \texttt{get-state} function queries data on the blockchain and returns the storage of a contract.
The \texttt{originate-contract} function results the contract's address on the blockchain. The program for a contract owner could be implemented by first deploying the contract, waiting 48 hours, and then calling the contract with the entrypoint \texttt{Unit} to close the contract.

\begin{lstlisting}[numbers=none]
address = orinigate-contract(script);
Time.sleep(to-second(48));
call-contract(address, Unit);
\end{lstlisting}

The bidding strategy could be implemented by first calling a contract with a minimum amount, watching the state of the contract, say every 5 minutes. If the bidder is not the current highest bidder and bidding is allowed, the bid has not reached the limit. He emits a contract call with a higher bid.

\begin{lstlisting}[numbers=none]
while get-state(address).flag = true and bid < limit do
    bid = bid + a;
    call_contract(address, bid);
    Time.speep(5);
done;
\end{lstlisting}

}
